---
title: 'Toronto Gardeners Survey Analysis: COVID-19'
author: "Shirin Arghandeh"
date: '2020-06-08'
geometry: "left=1cm,right=1cm,top=1cm,bottom=1cm"
output: pdf_document
---


```{r setup, include=FALSE}
library(readxl)
# Importing and reading survey data.
gardener_data <- read_excel("togardener_survey18.xls", col_names = TRUE)
str(gardener_data)
attach(gardener_data)
```

**Cross-Tabluations**

Cross-tabulation of types of garden on duration gardeners have grown food:
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(knitr)
library(kableExtra)

type_dur_clean <- gardener_data %>%
  dplyr::select(id = `Internal ID`, growing_duration, contains("_garden"))

# Transform so the two variables of interest (garden type and duration) are in two columns. 
# Each person will have 9 rows.
type_dur_long <- type_dur_clean %>%
  pivot_longer(contains("_garden"), names_to = "garden_type", values_to = "indicator") %>%
  replace_na(list(indicator = 0))

# Creating the table
td_cross <- type_dur_long %>%
  group_by(growing_duration, garden_type) %>%
  summarize(num = sum(indicator)) %>%
  pivot_wider(names_from = "garden_type", values_from = "num") %>%
  adorn_totals("row")

```
```{r echo=FALSE}
kable(td_cross) %>%
  kable_styling(latex_options = c("striped", "scale_down"))
```


Note: co-op garden has been integrated into other garden.


Testing for significance, we use Fisher's Exact Test to test the independence of variables garden type and Growing Duration. Our null hypothesis is that type of garden a gardener has is independent to the number of years a gardener has grown food.
```{r}
fisher.test(td_cross, simulate.p.value = TRUE,B=1e7)
```
Receiving error when workspace is set to $2e^7$ so tried simulating p-values based on number of Monte Carlo tests but this requires a very large number of simulations so p-value may not be accurate. It could be said that if $p<1e^{-7}$ the p-value is extremely small so we can reject the null hypothesis.


Cross tabulation of types of gardens on number of plants gardeners have grown:
```{r echo=FALSE, message=FALSE, warning=FALSE}
type_plant_clean <- gardener_data %>%
  dplyr::select(id = `Internal ID`, num_plants, contains("_garden"))

type_plant_long <- type_plant_clean %>%
  pivot_longer(contains("_garden"), names_to = "garden_type", values_to = "indicator") %>%
  replace_na(list(indicator = 0))

tp_cross <- type_plant_long %>%
  group_by(num_plants, garden_type) %>%
  summarize(num = sum(indicator)) %>%
  pivot_wider(names_from = "garden_type", values_from = "num") %>%
  adorn_totals("row")

```
```{r echo=FALSE}

kable(tp_cross) %>%
  kable_styling(latex_options = c("striped", "scale_down"))
```

Fisher's Exact Test for testing independence between garden type and number of plants grown.
```{r}
fisher.test(tp_cross, simulate.p.value=TRUE, B = 1e7)
```


Cross-tabulation of garden type versus where they get seeds.
```{r eval=FALSE, include=FALSE}
type_seed_clean <- gardener_data %>%
  dplyr::select(id = `Internal ID`,
                contains("_garden"), contains("_seed"))

type_seed_long <- type_seed_clean %>%
  pivot_longer(contains("_garden"), names_to = "garden_type") %>%
  pivot_longer(contains("_seed"), names_to = "get_seed", values_to = "indicator") %>%
  replace_na(list(indicator = 0))

ts_cross <- type_seed_long %>%
  group_by(get_seed, garden_type) %>%
  summarize(num = sum(indicator)) %>%
  pivot_wider(names_from = c("garden_type", "get_seed"), values_from = "num")

# # "Total" row
# type_seed_long %>%
#   group_by(garden_type) %>%
#   summarize(num = sum(indicator)) %>%
#   pivot_wider(names_from = "garden_type", values_from = "num")
```
